probKanren: A Simple Probabilistic extension for microKanren

### 2021-09-14 paper/main.tex
Fix notation

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Probabilistic programming is sometimes described as a generalisation
  of logic programming where instead of just returning a set of
  answers to a given query, we also return a probability distribution
  over those answers. But many contemporary probabilistic logic
  programming languages are not implemented as simple extensions of
  existing logic programming languages but instead involve their own
  unique implementations. Here we introduce probKanren, a simple
  extension to microKanren that transforms it into a probabilistic
  programming language without needing to make any modifications to
  the underlying search.
\end{abstract}

@@

\begin{minted}{Scheme}
  (run 1000 (q)
    (normal 0 3 q)
    (greatero q 0))
\end{minted}

\begin{minted}{Scheme}
  (run 1000 (q)
    (beta 1 1 q)
    (flip q #t))
\end{minted}

@@

Sequential Monte Carlo\cite{chopin2020introduction} are an efficient
online way to sample from probabilistic models especially suited for
state-space domains. If we imagine our probabilistic programs as
straight-line programs with no control-flow we can imagine numbering
every sample function $x_1, f_2, \ldots, f_n$ and every observe
function $g_1, g_2, \ldots, g_n$ then our probability density over our
random variables $x$ and observed data $y$ can be defined as:

@@

\begin{eqnarray}
  x_n &\sim& f(x_n \mid x_{0:n-1}) \\
  w_n^{(k)} &=& \frac{g(x_n \mid x_{0:n})f(x_n \mid x_{0:n-1})}{q(x_n \mid x_{0:n-1})} \\
  W_n^{(k)} &=& W_{n-1}^{(k)} w_n^{(k)}
\end{eqnarray}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Probabilistic programming can be conceptually seen as generalisation
  of logic programming where instead of just returning a set of
  answers to a given query, we also return a probability distribution
  over those answers. But many contemporary probabilistic logic
  programming languages implementations are not simple extensions of
  existing logic programming languages but instead involve their own
  unique implementations. Here we introduce probKanren, a simple
  extension to microKanren that transforms it into a probabilistic
  programming language without needing to make any modifications to
  the underlying logic language's search. We use several illustrative
  examples from the probabilistic programming and program synthesis
  literature to demonstrate the practicality of the approach.

\end{abstract}

@@

%TODO: Examples should use the grammar defined in the paper

\begin{minted}{Scheme}
  (run 1000 (q)
    (normal 0 3 q)
    (normal q 0 4))
\end{minted}

\begin{minted}{Scheme}
  (run 1000 (q)
    (beta 1 1 q)
    (bern q 1.0))
\end{minted}

@@

Sequential Monte Carlo\cite{chopin2020introduction} are an efficient
online way to sample from probabilistic models especially suited for
state-space domains. If we imagine our probabilistic programs as
straight-line programs with no control-flow we can imagine numbering
every sample function $f_1, f_2, \ldots, f_n$ and every observe
function $g_1, g_2, \ldots, g_n$ then our probability density over our
random variables $x$ and observed data $y$ can be defined as:

@@

\begin{eqnarray}
  x_n &\sim& f(x_n \mid x_{0:n-1}) \\
  w_n^{(k)} &=& \frac{g(y_n \mid x_{0:n})f(x_n \mid x_{0:n-1})}{q(x_n \mid x_{0:n-1})} \\
  W_n^{(k)} &=& W_{n-1}^{(k)} w_n^{(k)}
\end{eqnarray}
